### 2024-08-03 download-football-data.qmd
20240802 - fix indentation
20240802 - clean up player names for merging

```{r}
library("ffanalytics")
library("nflreadr")
library("nflfastR")
library("nfl4th")
library("nflplotR")
library("progressr")
library("lubridate")
library("tidyverse")
```

@@

```{r}
nfl_advancedStatsPFR_pass_seasonal <- nfl_advancedStatsPFR_pass_seasonal_raw %>% 
  mutate(
    nameMerge = toupper(str_remove_all(player, "[[:punct:]]"))
  ) %>% 
  rename(
    player_name.pass = player
  )

nfl_advancedStatsPFR_rush_seasonal <- nfl_advancedStatsPFR_rush_seasonal_raw %>% 
  mutate(
    nameMerge = toupper(str_remove_all(player, "[[:punct:]]"))
  ) %>% 
  rename(
    player_name.rush = player,
    age.rush = age,
    team = tm
  )

nfl_advancedStatsPFR_rec_seasonal <- nfl_advancedStatsPFR_rec_seasonal_raw %>% 
  mutate(
    nameMerge = toupper(str_remove_all(player, "[[:punct:]]"))
  ) %>% 
  rename(
    player_name.rec = player,
    age.rec = age,
    team = tm
  )

nfl_advancedStatsPFR_def_seasonal <- nfl_advancedStatsPFR_def_seasonal_raw %>% 
  mutate(
    nameMerge = toupper(str_remove_all(player, "[[:punct:]]"))
  ) %>% 
  rename(
    player_name.def = player,
    age.def = age,
    team = tm
  )

nfl_advancedStatsPFR_pass_weekly <- nfl_advancedStatsPFR_pass_weekly_raw %>% 
  mutate(
    nameMerge = toupper(str_remove_all(pfr_player_name, "[[:punct:]]"))
  ) %>% 
  rename(
    player_name.pass = pfr_player_name,
    season.pass = season,
    week.pass = week,
    team.pass = team
  )

nfl_advancedStatsPFR_rush_weekly <- nfl_advancedStatsPFR_rush_weekly_raw %>% 
  mutate(
    nameMerge = toupper(str_remove_all(pfr_player_name, "[[:punct:]]"))
  ) %>% 
  rename(
    player_name.rush = pfr_player_name,
    season.rush = season,
    week.rush = week,
    team.rush = team
  )

nfl_advancedStatsPFR_rec_weekly <- nfl_advancedStatsPFR_rec_weekly_raw %>% 
  mutate(
    nameMerge = toupper(str_remove_all(pfr_player_name, "[[:punct:]]"))
  ) %>% 
  rename(
    player_name.rec = pfr_player_name,
    season.rec = season,
    week.rec = week,
    team.rec = team
  )

nfl_advancedStatsPFR_def_weekly <- nfl_advancedStatsPFR_def_weekly_raw %>% 
  mutate(
    nameMerge = toupper(str_remove_all(pfr_player_name, "[[:punct:]]"))
  ) %>% 
  rename(
    player_name.def = pfr_player_name,
    season.def = season,
    week.def = week,
    team.def = team
  )

>>>>

```{r}
library("ffanalytics")
library("petersenlab")
library("nflreadr")
library("nflfastR")
library("nfl4th")
library("nflplotR")
library("progressr")
library("lubridate")
library("tidyverse")
```

@@

```{r}
nfl_advancedStatsPFR_pass_seasonal <- nfl_advancedStatsPFR_pass_seasonal_raw %>% 
  mutate(
    nameMerge = petersenlab::cleanUpNames(player)
  ) %>% 
  rename(
    player_name.pass = player
  )

nfl_advancedStatsPFR_rush_seasonal <- nfl_advancedStatsPFR_rush_seasonal_raw %>% 
  mutate(
    nameMerge = petersenlab::cleanUpNames(player)
  ) %>% 
  rename(
    player_name.rush = player,
    age.rush = age,
    team = tm
  )

nfl_advancedStatsPFR_rec_seasonal <- nfl_advancedStatsPFR_rec_seasonal_raw %>% 
  mutate(
    nameMerge = petersenlab::cleanUpNames(player)
  ) %>% 
  rename(
    player_name.rec = player,
    age.rec = age,
    team = tm
  )

nfl_advancedStatsPFR_def_seasonal <- nfl_advancedStatsPFR_def_seasonal_raw %>% 
  mutate(
    nameMerge = petersenlab::cleanUpNames(player)
  ) %>% 
  rename(
    player_name.def = player,
    age.def = age,
    team = tm
  )

nfl_advancedStatsPFR_pass_weekly <- nfl_advancedStatsPFR_pass_weekly_raw %>% 
  mutate(
    nameMerge = petersenlab::cleanUpNames(pfr_player_name)
  ) %>% 
  rename(
    player_name.pass = pfr_player_name,
    season.pass = season,
    week.pass = week,
    team.pass = team
  )

nfl_advancedStatsPFR_rush_weekly <- nfl_advancedStatsPFR_rush_weekly_raw %>% 
  mutate(
    nameMerge = petersenlab::cleanUpNames(pfr_player_name)
  ) %>% 
  rename(
    player_name.rush = pfr_player_name,
    season.rush = season,
    week.rush = week,
    team.rush = team
  )

nfl_advancedStatsPFR_rec_weekly <- nfl_advancedStatsPFR_rec_weekly_raw %>% 
  mutate(
    nameMerge = petersenlab::cleanUpNames(pfr_player_name)
  ) %>% 
  rename(
    player_name.rec = pfr_player_name,
    season.rec = season,
    week.rec = week,
    team.rec = team
  )

nfl_advancedStatsPFR_def_weekly <- nfl_advancedStatsPFR_def_weekly_raw %>% 
  mutate(
    nameMerge = petersenlab::cleanUpNames(pfr_player_name)
  ) %>% 
  rename(
    player_name.def = pfr_player_name,
    season.def = season,
    week.def = week,
    team.def = team
  )
